Unifrac tree

### 2019-11-15 scripts/23_unifrac.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(seqinr)
source('~/MSK/work/microbiome_db/SQL/scripts/get_data_from_query_OTU.R')
```

@@

```{r}
# create fasta file and write out to disk which will do the msa later
res <- apply(seqs, 1, function(Row){
  write.fasta(sequences = as.list(Row[['asv_sequence']]), 
              names = Row[['key']],
              file.out = str_glue('../output/ASV_fa/{Row[["key"]]}_ASV_seq.fa'))
})

# should be a fasta file with 80,000 sequences 
```

```{bash}
# do the msa
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(seqinr)
library("seqRFLP")
source('~/MSK/work/microbiome_db/SQL/scripts/get_data_from_query_OTU.R')
```

@@

```{r}
# should be a fasta file with 80,000 sequences 
res <- dataframe2fas(seqs %>% 
                       select(key, asv_sequence) %>% 
                       sample_n(20000), file="../output/all.fa")
```

```{bash}
# do the msa
# Fastest possible (nucleotides)
~/Downloads/SDE2/analysis/14_Day3/analysis/19_MSA/output/muscle -in ../output/all.fa -out ../output/all_msa_fast.fa -maxiters 1 -diags  
```

## Use QIIME to build the tree
